---
title: "Plots"
date: "13 maj 2020"
output: html_document
---

### Load Packages and Data
```{r}
library(pacman)
pacman::p_load(
  tidyverse,
  gridExtra,
  patchwork
)
### Load data ###
d000 <- read_csv("Results/saved_results_000.csv") %>% mutate(pb = 0)
d001 <- read_csv("Results/saved_results_001.csv") %>% mutate(pb = 1) 
d200 <- read_csv("Results/saved_results_200.csv") %>% mutate(pb = 0)
d201 <- read_csv("Results/saved_results_201.csv") %>% mutate(pb = 1)
d400 <- read_csv("Results/saved_results_400.csv") %>% mutate(pb = 0)
d401 <- read_csv("Results/saved_results_401.csv") %>% mutate(pb = 1)

#merge data
d <- rbind(d000, d001, d200, d201, d400, d401)         
d <- d %>% select(-c(X1))

### Load meta data ###
meta000 <- read_csv("Results/meta_analysis_results_000.csv") %>% mutate(pb = 0)
meta001 <- read_csv("Results/meta_analysis_results_001.csv") %>% mutate(pb = 1) 
meta200 <- read_csv("Results/meta_analysis_results_200.csv") %>% mutate(pb = 0)
meta201 <- read_csv("Results/meta_analysis_results_201.csv") %>% mutate(pb = 1)
meta400 <- read_csv("Results/meta_analysis_results_400.csv") %>% mutate(pb = 0)
meta401 <- read_csv("Results/meta_analysis_results_401.csv") %>% mutate(pb = 1)

#merge data
meta <- rbind(meta000, meta001, meta200, meta201, meta400, meta401) %>% mutate(analysis_type = "meta-analysis")

```







### Summaries
Creating summary table for appendix (pp, bglmm, and bskep)
```{r regular }
# Summary of estimates from last pp
d_last_pp <- d %>%  group_by(true_sex_cond, publication_bias) %>% 
  filter(expt == max(expt), analysis_type == "pp") %>% 
  summarise(
    estimate = b_sex_cond_med,
    CI_lower = b_sex_cond_lower,
    CI_upper = b_sex_cond_upper, 
    analysis_type = "pp"
    )

# Summary of estimates from bglmm and bskep
d_mean <- d %>% filter(analysis_type != "pp") %>% 
  group_by(true_sex_cond, publication_bias, analysis_type) %>% 
  summarize(
    estimate = mean(b_sex_cond_med),
    CI_lower = mean(b_sex_cond_lower),
    CI_upper = mean(b_sex_cond_upper)
  )

# Merging summaries
d_summarized <- rbind(d_last_pp, d_mean) %>% 
  mutate(
    dist = estimate - (boot::inv.logit(true_sex_cond) - 0.5),
    dist_lower = CI_lower - (boot::inv.logit(true_sex_cond) - 0.5),
    dist_upper = CI_upper - (boot::inv.logit(true_sex_cond) - 0.5)
  )

# Make pretty
d_summarized <- d_summarized[order(d_summarized$analysis_type, d_summarized$publication_bias, d_summarized$true_sex_cond),]

format_summarized <- d_summarized %>% 
  formattable()
```

Creating summary table for appendix (meta-analysis and pp)
```{r meta + pp}

# Summarizing estimates for metaanalysis 
meta_pp <- meta %>% rename(
    estimate = b_sex_cond_meta,
    CI_lower = b_sex_cond_lower_meta,
    CI_upper = b_sex_cond_upper_meta,
    true_sex_cond = true_effect
  ) %>% select(
    analysis_type, pb, estimate, CI_lower, CI_upper, true_sex_cond
  )

# Adding estimate from last pp (and ensuring correct scale)
meta_pp <- rbind(as.tibble(d_last_pp), meta_pp) %>% #see regular for d_last_pp
  mutate(
    dist = estimate - (boot::inv.logit(true_sex_cond) - 0.5),
    dist_lower = CI_lower - (boot::inv.logit(true_sex_cond) - 0.5),
    dist_upper = CI_upper - (boot::inv.logit(true_sex_cond) - 0.5)
  )

# Make table
meta_pp %>% formattable()
```

### Plots
Plot that compares estimates from bglmm, bskep, and pp across all experiments (without publication bias)
```{r figure 2}

# Remove data with publication bias
d_pb0 <- d[d$pb == 0,]

#### PLOTTING ####

# Plotting true effect 0
te0_pb0_plot <- ggplot(data = d_pb0[d_pb0$true_sex_cond == 0,]) + 
  geom_point(aes(x = expt, y = b_sex_cond_med, color = analysis_type), size = 1) +
  geom_errorbar(aes(x = expt, ymax = b_sex_cond_upper, ymin = b_sex_cond_lower, color = analysis_type, width = 1), alpha = 0.5, size = 0.8) +
  geom_line(aes(x = as.numeric(expt), y = (boot::inv.logit(true_sex_cond) - boot::inv.logit(true_base))), 
            color = 'black', size = 1) +
  scale_color_manual(values=c("goldenrod2", "seagreen4", "red")) +
  labs(x = "Experiment number", y = "Interaction Estimate", color = "Analysis Type")  + 
  ggtitle("A") + 
  theme_minimal()

# Plotting true effect 1
te1_pb0_plot <- ggplot(data = d_pb0[d_pb0$true_sex_cond == 1,]) + 
  geom_point(aes(x = expt, y = b_sex_cond_med, color = analysis_type), size = 1) +
  geom_errorbar(aes(x = expt, ymax = b_sex_cond_upper, ymin = b_sex_cond_lower, color = analysis_type, width = 1), alpha = 0.5, size = 0.8) +
  geom_line(aes(x = as.numeric(expt), y = (boot::inv.logit(true_sex_cond) - boot::inv.logit(true_base))), 
            color = 'black', size = 1) +
  scale_color_manual(values=c("goldenrod2", "seagreen4", "red")) +
  labs(x = "Experiment number", y = "Interaction Estimate", color = "Analysis Type") + 
  ggtitle("B") + 
  theme_minimal()

# Plotting true effect 2
te2_pb0_plot <- ggplot(data =  d_pb0[d_pb0$true_sex_cond == 2,]) + 
  geom_point(aes(x = expt, y = b_sex_cond_med, color = analysis_type), size = 1) +
  geom_errorbar(aes(x = expt, ymax = b_sex_cond_upper, ymin = b_sex_cond_lower, color = analysis_type, width = 1), alpha = 0.5, size = 0.8) +
  geom_line(aes(x = as.numeric(expt), y = (boot::inv.logit(true_sex_cond) - boot::inv.logit(true_base))), 
            color = 'black', size = 1) +
  scale_color_manual(values=c("goldenrod2", "seagreen4", "red")) +
  labs(x = "Experiment number", y = "Interaction Estimate", color = "Analysis Type") + 
  ggtitle("C") + 
  theme_minimal()


# Arranging plots
combined_te_pb0_plot <- te0_pb0_plot + te1_pb0_plot + te2_pb0_plot & theme(legend.position = "bottom")
combined_te_pb0_plot + plot_layout(guides = "collect")

```

Plot that compares distance from true effect of meta-analysis vs. pp (without publication bias)
```{r figure 3}

# Calculating distance from true effect
d$abs_dist <- abs(d$b_sex_cond_med - (boot::inv.logit(d$true_sex_cond)-boot::inv.logit(d$true_base))) #absolute distance
d$dist <- d$b_sex_cond_med - (boot::inv.logit(d$true_sex_cond)-boot::inv.logit(d$true_base)) #distance

# Calculating CIs
d$b_sex_cond_lower <- d$b_sex_cond_lower - (boot::inv.logit(d$true_sex_cond)-boot::inv.logit(d$true_base))
d$b_sex_cond_upper <- d$b_sex_cond_upper - (boot::inv.logit(d$true_sex_cond)-boot::inv.logit(d$true_base))


#### PLOTTING ####

ggplot(data = meta_pp[meta_pp$pb == 0,]) +  
  geom_point(aes(x = true_sex_cond, y = dist, color = analysis_type), size = 2) +
  geom_errorbar(aes(x = true_sex_cond, ymax = dist_upper, ymin = dist_lower, 
                    color = analysis_type), width = 0.1, alpha = 0.5, size = 1) +
  geom_line(aes(x = true_sex_cond, y = 0), 
            color = 'black', size = 1) +
  scale_color_manual(values=c("royalblue", "red")) +
  labs(x = "True Interaction Effect", y = "Distance from True Interaction Estimate", color = "Analysis Type") +
  theme_minimal()

```

Plot that compares distance from true effect of pp with/without publication bias
```{r publication bias}

#### PLOTTING ####

# pp distance from true effect (without publication bias)
pp_pb0_plot <- ggplot(data = d_pb0[d_pb0$analysis_type == "pp",], aes(x = expt, y = abs_dist, color = as.factor(true_sex_cond)), size = 1) + 
  geom_point() + geom_line(size = 0.3) +  
  scale_color_manual(values=c("cyan4", "darkgoldenrod1", "violetred2")) +
  labs(x = "Experiment number", y = "Distance from true effect", color = "True Effect",
       title = "A")  + 
  scale_y_continuous(limit= c(0, 0.11)) +
  theme_minimal() + theme(legend.position = "bottom") 

# pp distance from true effect (with publication bias)
pp_pb1_plot <- ggplot(data = d_pb1[d_pb1$analysis_type == "pp",], aes(x = expt, y = abs_dist, color = as.factor(true_sex_cond)), size = 1) + 
  geom_point() + geom_line(size = 0.3) + 
  scale_color_manual(values=c("cyan4", "darkgoldenrod1", "violetred2")) +
  labs(x = "Experiment number", y = "Distance from true effect", color = "True Effect", 
       title = "B")  + 
  scale_y_continuous(limit= c(0, 0.11)) +
  theme_minimal() + theme(legend.position = "bottom") 

# Arranging plots
pp_pb_plot <- pp_pb0_plot + pp_pb1_plot & theme(legend.position = "bottom")
pp_pb_plot + plot_layout(guides = "collect") 

```

